---
title: "L - Comparing Logistic Models"
author: "Anaan Choudhury"
format: pdf
---

##Question 1
```{r}
library(Stat2Data)
data("ICU")
```

```{r}
library(dplyr)
ICU <- mutate(ICU, AgeGroup = recode(AgeGroup,
                                     `1` = "Young",
                                     `2` = "Old",
                                     `3` = "Elderly"
                                    ),
              AgeGroup = factor(AgeGroup, levels = c("Young", "Old", "Elderly"))
              )
```

```{r}
age_and_bp_add <- glm(Survive ~ AgeGroup + SysBP, data=ICU, family=binomial)
age_and_bp_interaction <- glm(Survive ~ AgeGroup * SysBP, data=ICU, family=binomial)
```
age_and_bp_add is the reduced model because it is only additive. It doesn't account for effects of the coefficients on each other. 

##Question 2
```{r}
anova(age_and_bp_add, age_and_bp_interaction, test = "Chisq")
```
P-value = 0.6788
Very large, so we choose the reduced model. 
Interaction doesn't discrease variance enough to warrant making the model longer and more complex. We always aim to use simpler, basic models. 

##Question 3
H0 - Null: A person’s age group doesn’t have a significant impact on the effect of Blood Pressure on survival

HA - Alternative: A person’s age group does have a significant impact on the effect of Blood Pressure on survival



